
\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{fontawesome}

\pagestyle{empty}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}
\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubItem}[2]{\item\small{\textbf{#1}{: #2}}}
\renewcommand{\labelitemii}{$\circ$"}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
  {\Huge \textbf{Mayank Saxena}} \\
  \vspace{2pt}
  \href{mailto:mayanksaxena@example.com}{mayanksaxena@example.com} $|$
  +91-XXXXXXXXXX $|$
  \href{https://github.com/1xlblaze}{github.com/1xlblaze} $|$
  \href{https://linkedin.com/in/yourlinkedin}{linkedin.com/in/yourlinkedin}
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
Backend Developer with 3+ years of experience building scalable, distributed systems. Proficient in Golang, GCP, Kubernetes, and microservices. Proven ability to take ownership of complex backend systems, optimize performance, and lead cross-functional initiatives.

%-----------SKILLS-----------
\section*{Technical Skills}
\textbf{Languages:} Golang, Python, Java, C++ \\
\textbf{Frameworks/Tools:} Kubernetes, Docker, gRPC, Kafka, NATS, Redis, Git \\
\textbf{Databases:} PostgreSQL, MySQL, MongoDB \\
\textbf{Cloud:} Google Cloud Platform (GCP), AWS \\
\textbf{Other:} Microservices, CI/CD, System Design, REST, GitHub Actions

%-----------EXPERIENCE-----------
\section*{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {TartanHQ}{Dec 2021 -- Present}
  {Backend Engineer}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{Built and owned the complete Account Aggregator integration system with Go and GCP.}
    \resumeItem{Designed and implemented microservices for handling financial data securely.}
    \resumeItem{Optimized backend services resulting in a 30\% performance boost.}
    \resumeItem{Implemented logging, alerting, and monitoring pipelines using ELK stack.}
  \resumeItemListEnd

\resumeSubheading
  {OpsLyft}{May 2021 -- Nov 2021}
  {Backend Engineer}{Remote}
  \resumeItemListStart
    \resumeItem{Integrated Prometheus for system monitoring and Grafana dashboards.}
    \resumeItem{Worked on Infrastructure Cost Management systems using Python and Kubernetes.}
    \resumeItem{Contributed to infrastructure automation using Terraform and GitHub Actions.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section*{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Jaypee Institute of Information Technology}{2018 -- 2022}
  {B.Tech in Computer Science}{Noida, India}
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section*{Achievements}
\resumeItemListStart
  \resumeItem{Published multiple research papers on ML & NLP in IEEE and Scopus journals.}
  \resumeItem{Among top 5\% contributors on GitHub in open-source Go projects.}
  \resumeItem{Mentored juniors in backend development and DevOps practices.}
\resumeItemListEnd

%-----------PUBLICATIONS-----------
\section*{Publications}
\resumeItemListStart
  \resumeItem{Research on Emotion Detection using BERT – \textit{IEEE Access, 2021}}
  \resumeItem{Deep Learning-based COVID Spread Modelling – \textit{Elsevier, 2020}}
\resumeItemListEnd

\end{document}
